\thetitle

### 2013-04-17 tfpie/tfpie.tex
reorg
start on related

\subsection{Side-by-side example of program design}

@@

\begin{figure}
\begin{minipage}[t]{3.5in}
\begin{verbatim}
#lang bsl
;; A Tree is one of:
;; - (make-leaf Number)
;; - (make-node Tree Number Tree)
(define-struct leaf (v))
(define-struct node (left v right))

@@

@@

@@

\section{Our course}
\label{sec:our-course}

\subsection{Representation-independence and interface-oriented programming}

\subsection{Distributed, Interactive Programs}

@@

@@

\cite{dvanhorn:Chakravarty2004Risks}

\cite{dvanhorn:Ragde2008Chilling}

@@

>>>>

\subsection{Day 1}

@@

\begin{figure}[h!]
\begin{minipage}[t]{3.5in}
\begin{verbatim}
#lang bsl
;; A Tree is one of:
;; - (make-leaf Number)
;; - (make-node Tree Number Tree)
(define-struct leaf (v))
(define-struct node (left v right))

@@

\subsection{Worlds and animations}

@@

\subsection{Language levels}

No SE tools/mechanism built into the language.

\subsection{Universe}

\subsection{Programming to interfaces}

@@

@@

Teaching programming principles in a functional style has a long
history, with Abelson and Sussman's \emph{Structure and Interpretation
of Computer Programs}~\cite{dvanhorn:sicp} a prominent example.  Our
work follows in the tradition of the \emph{TeachScheme!} project, now
\emph{Program by Design} (PbD), which emphasizes a systematic
approach to program construction.

Since the introduction of functional-first curricula, and more
specifically in the Program by Design framework, numerous courses have
tackled the problem of transition.  Typically they, as we, transition
to Java in the second course.  We discuss first the approach developed
by some of the principal creators of PbD, and then other approaches.

\subsection{ProfessorJ}

@@

@@

\subsection{Other transitions}

\cite{dvanhorn:Ragde2008Chilling}
\cite{dvanhorn:Chakravarty2004Risks}

\subsection{Other approaches to Java}
